---
title: "Car MPG Prediction"
author: "Olusegun Oyedele"
date: "9/16/2021"
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application

Using the data provided by mtcars dataset, we fit a linear model to predict MPG based on displacement and horsepower.

The application is running on (https://t513l6-olusegun-oyedele0adeyi.shinyapps.io/MPG-Milesgallon-Prediction/)

ui.R, and Server.R Code in my github repository (https://github.com/adeyisegun/car-MPG-prediction)

## mtcars Dataset

The data used in the app comes from the mtcars dataset. 

```{r summary}
data(mtcars)
summary(mtcars)
```

## Plot
In the scatterplot below are represented the data used for the prediction model
```{r plot}
data(mtcars)
plot(jitter(mtcars$mpg) ~ mtcars$disp,xlab="Displacement",ylab="MPG",
     main="Scatterplot of mtcars Data",pch=19,frame.plot=FALSE,
     col=ifelse(mtcars$am==1, "red", "blue"))
```

